---
title: "R Exercises Session 8"
author: "Michael Brancato"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

First, clone the [Assignment8][1] repository to your own GitHub account
by forking. Look for the forking button on the GitHub repository page.

You can then modify the repository (namely the `R_Exercises8.Rmd` file)
and complete the assignment by adding your answers in the appropriate
place. Do **NOT** rename the file.

## Completing the assignment

Check your work by knitting the document.

1. Create a level 2 header below in Markdown with the name "Answer 1".

## Answer 1

2. Add an unordered Markdown list of your favorite food dishes and
add their ingredients as sub-items in the list. You should enter at least two
dishes with two ingredients each.

-   pizza

    -   dough

        -   flour

        -   water

        -   salt

    -   tomato sauce

        -   canned diced tomatoes

        -   diced onion

        -   minced garlic

        -   salt

        -   pepper

        -   oregano

        -   basil

        -   red wine

    -   mozzarella cheese

-   fish tacos

    -   flour tortilla

        -   flour

        -   water

        -   salt

    -   filling

        -   shredded white fish

        -   chili powder

        -   lime juice

        -   cumin

    -   lettuce

    -   chopped tomato

    -   diced pickled jalapeño

    -   hot sauce

        -   vinegar

        -   habañero pepper

3. Insert an R code chunk below. Show the `summary` of the `Orange` dataset.
Run a linear regression using the `lm` function to predict `circumference` from
`age` and assign the result. Show the `summary` of the fit object that you
assigned.

```{r}
data(Orange)
library(dplyr)
Orange %>% group_by(Tree) %>% summarize(mean = mean(circumference))

tree_lm <- lm(circumference ~ age, data = Orange)

Or_result <- predict(tree_lm, data.frame(age = mean(Orange$age)), interval = "predict")

tree_lm

cat("The circumference of an orange tree at the mean age of this study,")
mean(Orange$age)
cat("days, is predicted to be (in mm): ")
Or_result

```

4. Add an RMarkdown weblink (in link format) below to your favorite R reference
website.

[Pandoc Markdown](https://rmarkdown.rstudio.com/authoring_pandoc_markdown.html)

5. Replace the author field in the `yaml` header with your name and then
successfully `knit` the RMarkdown document into a Word document.


6. Follow the [Pull Request instructions on GitHub](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork)
to submit your assignment via GitHub as a Pull Request to the [Assignment8][1]
repository.

[1]: https://github.com/CUNYSPHCode/Assignment8

